Commutative Character Sheaves on smooth group schemes over finite fields

### 2016-01-28 followup.tex
Fixed a few typos

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
%
In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of the Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.

@@

\begin{conjecture}\label{conj:Jacobi}
For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as in Section~\ref{sec:Jacobi}, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
\end{conjecture}

@@

Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
\begin{enumerate}
\item[(0)] a sequence of compact groups 
\[
\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K;
\]
\item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
\item[(2)] a quasicharacter $\varphi_i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\varrho, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.

@@

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
\end{equation}
of $\,^\circ K^i \ltimes J^{i+1}$.
By construction, the character of this representation satisfies
\begin{equation}\label{eq:tilderho}
\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(h_{i+1}(y))\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi_i(p_i(y))
\end{equation}
for $y \in \,^\circ K^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$. 
This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}
%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
%\[
%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi_0(k_0) \cdots \varphi_d(k_d),
%\]
%for $k_i\in J^i$.

@@

We may now revisit the ingredients in the construction of the representation $\,^\circ \rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled at the beginning of this section.
\begin{enumerate}
\item The continuous representation $\varrho$ of $\,^\circ K^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$. 
Let $\tau$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\tau$ is itself obtained by pulling back a representation $\sigma$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
\item Quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
\item The representation $h_{i+1}^*(W_{i+1})$ of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK)$ is obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}
Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}

In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi_0, \ldots , \varphi_d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.

@@

Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \sim \EE$.

@@

By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \sigma.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \tau.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}. 
With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
Factor
\[
\begin{tikzcd}
\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \EE \\
& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
\end{tikzcd}
\]
Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
\[
\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.

@@

Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
&& G_m^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
\[
(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
Consider the sheaf 
\[
\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
\[
\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
\]
%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
Then
\begin{eqnarray*}
\trFrob{\cs{\tilde A}^{i+1}_m}(x)
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
\end{eqnarray*}
Comparing with \eqref{eq:tilderho}, we see that 
\[
y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
\]
is precisely the function obtained by factoring the character of $\,^\circ {\tilde \rho}_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$. 
In particular, this is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
It follows that 
\[
\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\,^\circ \rho_{i+1})
\]
on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.\todo{Hmm... Homomorphism?}
\todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$.
%
This completes the inductive definition of $\cs{A}_m^i$ with the desired property.

@@

%\item 
For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$.

@@

For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$.

>>>>

As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
Let us refer to the types arising in this manner as {\it Yu types}.
%In this section we show that every Yu type is geometrizable.
% in a sense which will be made clear below.
%
A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
%
In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.

@@

\begin{conjecture}\label{conj:Jacobi}
For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as above, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
\end{conjecture}

@@

Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
\begin{enumerate}
\item[(0)] a sequence of compact groups 
\[
\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K;
\]
\item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
\item[(2)] a quasicharacter $\varphi^i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
The representations $(\varrho, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.

@@

The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
Suppose $i=0, \ldots, d-1$.
The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
\begin{equation}\label{eq:semiprod}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
&& \,^\circ K^{i+1} \arrow{d}{} && \\
&& 1 &&
\end{tikzcd}
\end{equation}
Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
Write $\inf(\,^\circ\rho_i \otimes \varphi^i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$. 
Consider the representation
\begin{equation}\label{eq:tensor}
\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi^i)
\end{equation}
of $\,^\circ K^i \ltimes J^{i+1}$.
By construction, the character of this representation satisfies
\begin{equation}\label{eq:tilderho}
\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi^i(p_i(y))
\end{equation}
for $y \in \,^\circ K^i \ltimes J^{i+1}$.
By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$. 
This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi^d$, so this can't be quite right.}
%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
%\[
%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
%\]
%for $k_i\in J^i$.

@@

We may now revisit the ingredients in the construction of the representation $\,^\circ \rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled at the beginning of this section.
\begin{enumerate}
\item The continuous representation $\varrho$ of $\,^\circ K^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$. 
Let $\tau$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
In fact, $\tau$ is itself obtained by pulling back a representation $\sigma$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
\item Quasicharacters $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
\item The representation $h_{i+1}^*(W_{i+1})$ of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK)$ is obtained by pulling back a representation along 
\[
(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
\]
Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
\[
\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
\]
\end{enumerate}
Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
\begin{quotation}
{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
 the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$. These results suggest that algebraic geometry and group schemes should play an
important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
\end{quotation}

In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.

@@

Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \approx \EE$.

@@

By continuity of the quasicharacters $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
\[
\begin{tikzcd}
\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
\end{tikzcd}
\] 
for each $i=0, \ldots d$.\todo{Fix notation: $\phi$ to $\varphi$}
Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
\[
\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
\]
%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.

By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
\[
\trFrob{A} = \trace \sigma.
\]
(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
Then 
\[
\trFrob{A^0} = \trace \tau.
\]
The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{CR}*{\S 4.3}. 
With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
Factor
\[
\begin{tikzcd}
\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \EE \\
& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
\end{tikzcd}
\]
Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
\[
\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
\]
%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.

@@

Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
\begin{equation}\label{eq:pi}
\begin{tikzcd}
\ && 1 \arrow{d} && \\
\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
&& G_m^{i+1} \arrow{d} && \\
&& 1 && 
\end{tikzcd}
\end{equation}
where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
\[
(p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
Consider the sheaf 
\[
\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
\]
on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define \todo{Reference needed here.}
\[
\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
\]
%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
Then
\begin{eqnarray*}
\trFrob{\cs{\tilde A}^{i+1}_m}(x)
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i}(y)).
\end{eqnarray*}
Comparing with \eqref{eq:tilderho}, we see that 
\[
y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i}(y))
\]
is precisely the function obtained by factoring the character of $\,^\circ {\tilde \rho}_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$. 
In particular, this is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
It follows that 
\[
\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\,^\circ \rho_{i+1})
\]
on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$. \todo{Hmm... Homomorphism?}
\todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$. 
%
This completes the inductive definition of $\cs{A}_m^i$ with the desired property.

@@

%\item 
For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi^i$ of $\underline{G}^i(\OK)$.

@@

For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$.
